---
title: "Results Analysis Paper 2"
author: "Montserrat Valdivia"
date: 'March 2023'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list=ls())
#load libraries
library("tidyverse")
library(dplyr)
library(purrr)
library("R.utils")
library(jtools)
library(extrafont)
library(gridExtra)

```


# 1. Proficiency parameter recovery 


```{r}
# Read in data 
# path = "C:/Users/Montse/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Results/"
# 
# setwd(paste0(path, "Data/"))
# 
# files = dir(pattern = ".Rbin*")
# 
# all_results <- files %>%
#    map(loadObject) %>%
#    reduce(bind_rows)
# 
# all_results = all_results %>%
#   mutate(cntry = case_when(country %in% c(1:3) ~ "Low",
#                            country %in% c(4:6) ~ "Medium",
#                            country %in% c(7:9) ~ "High"),
#          condition = case_when(cond == 1 ~ "OG",
#                                cond == 2 ~ "+2E",
#                                cond == 3 ~ "+2H",
#                                cond == 4 ~ "+2E&H",
#                                cond == 5 ~ "+4E",
#                                cond == 6 ~ "+4H",
#                                cond == 7 ~ "+4E&H",
#                                cond == 8 ~ "+6E",
#                                cond == 9 ~ "+6H",
#                                cond == 10 ~ "+6E&H")) %>%
#   mutate(cntry = factor(cntry, levels = c( "High","Medium","Low" )),
#          condition = factor(condition, levels = c("OG","+2E","+4E","+6E","+2H","+4H","+6H","+2E&H","+4E&H","+6E&H"))) %>%
#   
#   
# 
# 
# saveObject(all_results, file = "C:/Users/Montse/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Results/Results PV.RData")

#a = loadObject(paste0(path, "Data/data_GAT_cond1_r1.Rbin"))
```

```{r}
all_results = loadObject("C:/Users/Montse/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Results/Results PV.RData")

```



```{r}
all_results_v2 = all_results %>%
  select(rep, design, country, cntry, condition, 
         TH0, PV, se.Dim1) %>%
  mutate(bias = PV - TH0, 
         bias_sq = bias^2)

res = all_results_v2 %>%
  group_by(design, condition, cntry) %>%
  summarise(TH0 = mean(TH0),
            bias = mean(bias),
            rmse = sqrt(mean(bias_sq)),
            se = mean(se.Dim1),
            abias = abs(bias) )
correlation = all_results %>%
  group_by(design, condition, cntry) %>%
  summarize(cor = cor(TH0, PV))


res1 = res %>%
  filter(condition == "OG" & design == "Random")%>%
  select(design, condition, cntry, se)
  
res2 = res %>%
  filter(condition != "OG")%>%
  select(design, condition, cntry, se)

res3 = left_join(res2, res1, by = c( "cntry"))
res31 = res3 %>%
  mutate(ef_gain = (se.x - se.y)/se.y)

```

## 1.1. Bias

Primary observations:
positive bias = overestimation of proficiency 
- High performing countries have negative bias
- when easier booklets are introduced that is the closest to zero bias (positive bias) for high performing countries
- positive bias when easier booklets are introduced for medium countries
- positive bias when easier items are introduced
- negative bias when harder booklets are introduced 
- random assignment has lesser bias than GAT in general *  is this design really adaptive ?

```{r}
ggplot(data = res, 
       mapping=aes(x=condition, y=bias, shape = design, 
                  # shape = `Country`
                  ))+
 # geom_boxplot()+
  geom_hline(aes(yintercept = 0), linetype = "dashed", color ="grey" )+ 
  stat_summary(fun.y=mean,   size=.5, position = position_dodge(0.75)) +
  facet_grid(  cntry ~ .)+
  labs( x = "Additional Booklets Difficulty" , y= "Proficiency Bias", shape = "Test Design")+
  #ylim(-.5, .5)+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 16, family = "Times New Roman"))
  ggsave(filename = paste0("W:/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Graphs/",
                      "Proficiency Bias.tiff"), device = "tiff",
   width = 35, height = 20, units = "cm", dpi = 600, compression = "lzw+p")
```

## 1.2. RMSE

```{r}
ggplot(data = res, 
       mapping=aes(x=condition, y=rmse, shape = design
                  ))+
  #geom_point()+
  geom_hline(aes(yintercept = 0), linetype = "dashed", color ="grey" )+ 
  stat_summary(fun.y=mean,   size=.5, position = position_dodge(0.75)) +
  facet_grid(  cntry ~ .)+
  labs( x = "Additional Booklets Difficulty" , y= "Proficiency RMSE", shape = "Test Design")+
  ylim(0, .5)+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 16, family = "Times New Roman"))
  ggsave(filename = paste0("W:/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Graphs/",
                      "Proficiency RMSE.tiff"), device = "tiff",
   width = 35, height = 20, units = "cm", dpi = 600, compression = "lzw+p")
```

## 1.3. Correlation 

```{r}
ggplot(data = correlation, 
       mapping=aes(x=condition, y=cor, shape = design
                  ))+
  #geom_point()+
 # geom_hline(aes(yintercept = 0), linetype = "dashed", color ="grey" )+ 
  stat_summary(fun.y=mean,   size=.5, position = position_dodge(0.75)) +
  facet_grid(  cntry ~ .)+
  labs( x = "Additional Booklets Difficulty" , y= "Generated and Estimated Proficiency Correlation", shape = "Test Design")+
  ylim(0.9, 1)+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 16, family = "Times New Roman"))
  ggsave(filename = paste0("W:/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Graphs/",
                      "Proficiency Correlation.tiff"), device = "tiff",
   width = 35, height = 20, units = "cm", dpi = 600, compression = "lzw+p")
```

# 4. Standard Error Proficiency

```{r}
ggplot(data = all_results, 
       mapping=aes(x=condition, y=se.Dim1, shape = design
                  ))+
  geom_boxplot()+
 # geom_hline(aes(yintercept = 0), linetype = "dashed", color ="grey" )+ 
  stat_summary(fun.y=mean,   size=.5, position = position_dodge(0.75)) +
  facet_grid(  cntry ~ .)+
  labs( x = "Additional Booklets Difficulty" , y= "Proficiency Standard Error", shape = "Test Design")+
 # ylim(0.9, 1)+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 16, family = "Times New Roman"))
  ggsave(filename = paste0("W:/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Graphs/",
                      "Proficiency SE.tiff"), device = "tiff",
   width = 35, height = 20, units = "cm", dpi = 600, compression = "lzw+p")
```

# 2. Item Parameter 

```{r}

# Read in data 
path = "C:/Users/Montse/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Results/"

#a = loadObject(paste0(path, "Items/items_GAT_cond1_r1.Rbin"))

setwd(paste0(path, "Items/"))

files = dir(pattern = ".Rbin*")

items_results <- files %>%
   map(loadObject) %>%
   reduce(bind_rows)

item_results = items_results %>%
  mutate( condition = case_when(condition == 1 ~ "OG",
                               condition == 2 ~ "+2E",
                               condition == 3 ~ "+2H",
                               condition == 4 ~ "+2E&H",
                               condition == 5 ~ "+4E",
                               condition == 6 ~ "+4H",
                               condition == 7 ~ "+4E&H",
                               condition == 8 ~ "+6E",
                               condition == 9 ~ "+6H",
                               condition == 10 ~ "+6E&H")) %>%
  mutate(condition = factor(condition, levels = c("OG","+2E","+4E","+6E","+2H","+4H","+6H","+2E&H","+4E&H","+6E&H")),
         Passage.Name = factor(Passage.Name, levels = c("How Did We Learn to Fly?", "Hungry Plant", "Icelandic Horses",
                                                        "Library Mouse", "Oliver and The Griffin", "Pemba Sherpa", 
                                                        "Sharks", "Shiny Straw", "The Empty Pot", "The Summer My Father Was 10", 
                                                        "Training A Deaf Polar Bear", "Where's the Honey?",
                                                        "New Passage Inf D3","New Passage Inf D4","New Passage Inf D5",
                                                        "New Passage Lit D3","New Passage Lit D4","New Passage Lit D5",
                                                        "New Passage Inf E4","New Passage Inf E5","New Passage Inf E6",
                                                        "New Passage Lit E4","New Passage Lit E5","New Passage Lit E6" )))
  


saveObject(item_results, file = "C:/Users/Montse/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Results/Results Items.RData")


item_results1 = item_results %>%
  mutate(bias2_a = bias_a^2,
         bias2_b = bias_b^2,
         cor_a = cor(Slope..aj., rs_est_a),
         cor_b = cor(Location..bj., rs_est_b))


item_results_it = item_results1 %>%
  group_by(ItemID_og, Passage.Name, design, condition) %>%
  summarise(bias_a = round(mean(bias_a),3),
            bias_b = round(mean(bias_b),3),
            rmse_a = round(sqrt(mean(bias2_a)),3),
            rmse_b = round(sqrt(mean(bias2_b)),3),
            cor_a  = round(mean(cor_a),3),
            cor_b  = round(mean(cor_b),3))

item_results_ps = item_results1 %>%
  group_by(Passage.Name, design) %>%
  summarise(a = mean(rs_est_a),
            bias_a = round(mean(bias_a),3),
            rmse_a = round(sqrt(mean(bias2_a)),3),
            cor_a  = round(mean(cor_a),3),
            b = mean(rs_est_b),
            bias_b = round(mean(bias_b),3),
            rmse_b = round(sqrt(mean(bias2_b)),3),
            cor_b  = round(mean(cor_b),3))

item_results_psO = item_results1 %>%
  group_by(Passage.Name) %>%
  summarise(a = mean(alpha),
            b = mean(beta),
            bias_a = round(mean(bias_a),3),
            bias_b = round(mean(bias_b),3),
            rmse_a = round(sqrt(mean(bias2_a)),3),
            rmse_b = round(sqrt(mean(bias2_b)),3),
            cor_a  = round(mean(cor_a),3),
            cor_b  = round(mean(cor_b),3))

item_results_new = item_results[grepl("New", item_results$Passage.Name),]

library(writexl)
write_xlsx(item_results_ps,paste0(path, "Item parameter table.xlsx"))


```

I think a table will be more productive here. 

## 2.1. IP Bias

```{r}
ggplot(data = item_results_ps, 
       mapping=aes(x=Passage.Name , y=bias_b, shape = condition
                  ))+
 # geom_boxplot()+
  geom_hline(aes(yintercept = 0), linetype = "dashed", color ="grey" )+ 
  stat_summary(fun.y=mean,   size=.5, position = position_dodge(0.75)) +
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10))+
  facet_grid( design ~ .)+
  labs( x = "Additional Booklets Difficulty" , y= "Passage - Difficulty Parameter Bias", shape = "Test Design")+
  ylim(-.05, .05)+
  theme_apa(legend.use.title = TRUE)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=1))+
  theme(text = element_text(size = 12, family = "Times New Roman"))
  ggsave(filename = paste0("C:/Users/Montse/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Graphs/",
                      "Difficulty bias.tiff"), device = "tiff",
   width = 35, height = 20, units = "cm", dpi = 600, compression = "lzw+p")
```


## 2.2. IP RMSE
```{r}

```

## 2.3. IP Cor
```{r}

```


# 3. Test Information

```{r}

# Read in data 
path = "C:/Users/Montse/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Results/"


```


```{r}

des = rep(c("GAT", "Random"), each = 10)

data_results = data.frame(design = des,
                          cond = rep(seq(1,10), each = des))

test_information_mean = function(cc, design){
  
  setwd(paste0(path, "Item Info/"))
  files = dir(pattern = paste0("testInfo_", design, "_cond", cc, "_"))
  test_info <- files %>%
   map(loadObject) %>%
   reduce(rbind)

  TImean = colMeans(test_info)

  
  plot(TImean)
  return(TImean)
}  
  
td = c("GAT", "Random")

for (cc in 1:10){
  for (tt in 1:2) {
    
    design = td[tt]
    TImean = test_information_mean(cc, design)
    data_results[data_results$cond == cc & data_results$design == design, 3:(2+length(TImean))] <- TImean
  }
}

theta = seq(-6,6, by = .1)
length(theta)

names(data_results)[3:121] <- theta

melt_results = reshape2::melt(data_results, id = c("design", "cond"))
names(melt_results)[3] <- "Theta"
names(melt_results)[4] <- "Test_Info"




melt_results = melt_results %>%
  mutate( cond = case_when(cond == 1 ~ "OG",
                               cond == 2 ~ "+2E",
                               cond == 3 ~ "+2H",
                               cond == 4 ~ "+2E&H",
                               cond == 5 ~ "+4E",
                               cond == 6 ~ "+4H",
                               cond == 7 ~ "+4E&H",
                               cond == 8 ~ "+6E",
                               cond == 9 ~ "+6H",
                               cond == 10 ~ "+6E&H")) %>%
  mutate(cond = factor(cond, levels = c("OG","+2E","+4E","+6E","+2H","+4H","+6H","+2E&H","+4E&H","+6E&H")))

a
```





```{r}


a = melt_results %>%
  filter(design == "GAT" & cond %in% c("OG", "+2E")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

b = melt_results %>%
  filter(design == "GAT" & cond %in% c("OG", "+4E")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

c = melt_results %>%
  filter(design == "GAT" & cond %in% c("OG", "+6E")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")
  
d = melt_results %>%
  filter(design == "GAT" & cond %in% c("OG", "+2H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

e = melt_results %>%
  filter(design == "GAT" & cond %in% c("OG", "+4H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

f = melt_results %>%
  filter(design == "GAT" & cond %in% c("OG", "+6H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

g = melt_results %>%
  filter(design == "GAT" & cond %in% c("OG", "+2E&H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")


h = melt_results %>%
  filter(design == "GAT" & cond %in% c("OG", "+4E&H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

i = melt_results %>%
  filter(design == "GAT" & cond %in% c("OG", "+6E&H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

figure = ggarrange(a,b,c,d,e,f,g,h,i,
                   ncol = 3, nrow = 3)

annotate_figure(figure, 
                bottom = text_grob("Proficiency Continuum", family = "Times New Roman", size = 14),
                left = text_grob("Test Information", rot = 90, family = "Times New Roman", size = 14))

ggsave(filename = paste0("C:/Users/Montse/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Graphs/",
                      "Test Information GAT.tiff"), device = "tiff",
   width = 35, height = 20, units = "cm", dpi = 600, compression = "lzw+p")


```

```{r}
a = melt_results %>%
  filter(design == "Random" & cond %in% c("OG", "+2E")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

b = melt_results %>%
  filter(design == "Random" & cond %in% c("OG", "+4E")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

c = melt_results %>%
  filter(design == "Random" & cond %in% c("OG", "+6E")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

d = melt_results %>%
  filter(design == "Random" & cond %in% c("OG", "+2H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

e = melt_results %>%
  filter(design == "Random" & cond %in% c("OG", "+4H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

f = melt_results %>%
  filter(design == "Random" & cond %in% c("OG", "+6H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

g = melt_results %>%
  filter(design == "Random" & cond %in% c("OG", "+2E&H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")


h = melt_results %>%
  filter(design == "Random" & cond %in% c("OG", "+4E&H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

i = melt_results %>%
  filter(design == "Random" & cond %in% c("OG", "+6E&H")) %>%
  ggplot( aes(x = Theta, y = Test_Info, shape = cond))+
  geom_point()+
  ylim(0,70)+
  labs(x = " ", y = " ", shape = " ")+
  scale_shape_manual(values = c(0,15))+
  scale_x_discrete(breaks = c(-6,-4,-2,0,2,4,6))+
  theme_apa(legend.use.title = TRUE)+
  theme(text = element_text(size = 12, family = "Times New Roman"))+
  theme(legend.position= c(0.15,.7), legend.direction = "vertical")

figure = ggarrange(a,b,c,d,e,f,g,h,i,
                   ncol = 3, nrow = 3)

annotate_figure(figure, 
                bottom = text_grob("Proficiency Continuum", family = "Times New Roman", size = 14),
                left = text_grob("Test Information", rot = 90, family = "Times New Roman", size = 14))

ggsave(filename = paste0("C:/Users/Montse/OneDrive - Indiana University/Dissertation/Data Analysis/Paper 2/Graphs/",
                         "Test Information Random.tiff"), device = "tiff",
       width = 35, height = 20, units = "cm", dpi = 600, compression = "lzw+p")
```
Improvements 

```{r}
melt_results_og = melt_results[-c(2381:2420),] %>%
  filter(cond == "OG")
melt_results_add = melt_results[-c(2381:2420),] %>%
  filter(cond != "OG")

melt_results_comp = left_join(melt_results_add, melt_results_og, by = c("design", "Theta")) 
melt_results_comp = melt_results_comp %>%
  mutate(comp = Test_Info.x - Test_Info.y)
  
a = melt_results_comp[melt_results_comp$comp >= 1,]
head(a)
tail(a, 80)
```

